\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
    \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule\vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
    \item\small{
        {#1 \vspace{-2pt}}
    }
}

\newcommand{\resumeSubheading}[4]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
        \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubheadingTitleOnly}[2]{
    \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
        \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
        \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in,
            label={}]}
        \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
        \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\huge \scshape Owen Cooke} \\ \vspace{1pt}
    \small 415-410-0316 $|$
    \href{mailto:owencooke15@gmail.com}{\underline{owencooke15@gmail.com}} $|$
    \href{https://www.linkedin.com/in/owenscooke/}
    {\underline{linkedin.com/in/owenscooke}}
    $|$
    \href{https://github.com/owencooke}{\underline{github.com/owencooke}}
\end{center}

%-----------EDUCATION-----------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{University of Alberta}{Sep 2020 -- Jun 2025}
{Bachelor of Science in Computer Engineering Co-op -- Software
    Option}{3.96 GPA}
\resumeItemListStart
\resumeItem{Scholarships: Superior Undergraduate Achievement (2022-24),
    Jason Lang (2021-23)}
\resumeItem{Coursework: Data Structures, Algorithms, Operating Systems,
    Databases, Data Analysis and Machine Learning}
\resumeItemListEnd
\resumeSubHeadingListEnd

%
%-----------PROGRAMMING SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
                    \textbf{Programming Languages}{: TypeScript, JavaScript
                        Java, Python, HTML/CSS, SQL
                        C/C++, Rust} \\
                    \textbf{Frameworks \& Tools}{: React, Node, Spring,
                        Expo, PostgreSQL, Jest, JUnit,
                        Playwright, AWS, Kibana, Docker,
                        Git} \\

              }}
\end{itemize}

%-----------EXPERIENCE-----------
\section{Experience}
\resumeSubHeadingListStart
\resumeSubheading
{NimbleRx}{Sep 2025 -- Present}
{Software Engineer}{Redwood City, CA}
\resumeItemListStart
\resumeItem{Designing and implementing Spring services and React features to deliver product enhancements for pharmacists.}
\resumeItem{Investigating production issues via Kibana log and SQL analysis and resolving, reducing pharmacy pain points.}
\resumeItemListEnd

\resumeSubheading
{NimbleRx}{Sep 2024 -- Dec 2024}
{Software Engineer Intern}{Redwood City, CA}
\resumeItemListStart
\resumeItem{Created an audit tool for downloading Stripe
    transactions using React, unblocking the launch of \textbf{85} pharmacies.}
\resumeItem{Refactored REST
    APIs
    and frontend flows to eliminate \textbf{85,000} improper
    404 errors/day, improving observability.}
\resumeItem{Optimized Amazon S3 integrations via Spring and AWS
    SDK, reducing file
    upload time by \textbf{30\%} platform-wide.}
\resumeItemListEnd

\resumeSubheading
{RBC Royal Bank}{May 2024 -- Aug 2024}
{Software Developer Intern}{Toronto, ON}
\resumeItemListStart
\resumeItem{Filed a patent for an LLM transcription tool to automate incident documentation for more intelligent IT insights.}
\resumeItem{Built real-time incident resolution tracking with WebSockets and MongoDB to visualize SRE response timelines.}
\resumeItemListEnd

\resumeSubheading
{ATB Financial}{May 2023 -- Aug 2023}
{Software Developer Intern}{Edmonton, AB}
\resumeItemListStart
\resumeItem{Wrote APIs for managing site banners with Node and
    Postgres, eliminating weekly manual code deployments.}
\resumeItem{Implemented an internal React tool for improved banner UX via  scheduling, emergency override, and history logs.}
\resumeItemListEnd

\resumeSubheading
{SMART LAB}{May 2022 -- Apr 2023}
{Software Research Assistant}{Edmonton, AB}
\resumeItemListStart
\resumeItem{Built a 3D app in Python to integrate with a simulated robotic cell for visualizing automated wear repair of pipes.}
    \resumeItem{Published an IEEE paper proposing a new 3D-scan feature
    extraction algorithm for re-manufacturing automation.}
\resumeItem{Developed a desktop app via Python and Qt for detecting 3D
    print defects from 3D scans to improve part quality.}
\resumeItemListEnd

\resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
{\textbf{\href{https://github.com/owencooke/memento}{\underline{Memento}}}
    $|$ \emph{React Native, FastAPI, PostgreSQL, Google Cloud}}{Jan 2025 -- Apr 2025}
\resumeItemListStart
\resumeItem{Created a mobile app to easily preserve keepsakes with image metadata, classification, and background removal.}
\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://github.com/owencooke/what-to-code}{\underline{What to
                Code}}}
    $|$
    \emph{Next.js, PostgreSQL, LangChain,
        OpenAI}}{Jun 2024 -- Dec 2024}
\resumeItemListStart
\resumeItem{Launched an LLM-powered platform to help
    coders brainstorm ideas and kickstart repositories via GitHub's API.}

\resumeItemListEnd

\resumeProjectHeading
{\textbf{\href{https://github.com/owencooke/mobility-mate}{\underline{MobilityMate}}}
    $|$
    \emph{React, Flask, OpenAI}}{Jan 2024}
\resumeItemListStart
\resumeItem{Implemented an AI voice assistant to support senior
    physiotherapy patients through their exercises.}
\resumeItem{Won 1st Place for the Diversity in Engineering Prize at
    HackED 2024 for promoting accessibility.}
\resumeItemListEnd
\resumeSubHeadingListEnd

%-----------VOLUNTEERING-----------
\section{Volunteering}
\resumeSubHeadingListStart
\resumeSubheadingTitleOnly
{Western Engineering Competition 2026}{May 2025 -- Sep 2025}
\resumeItemListStart
\resumeItem{Designed challenge prompt, rubric, and presentation materials as co-director of programming category.}
\resumeItemListEnd

\resumeSubheadingTitleOnly
{Computer Engineering Club}{Sep 2023 -- Sep 2024}
\resumeItemListStart
\resumeItem{Redesigned club website in React to improve visibility of
    events and technical resources for engineering students.}
\resumeItem{Established partnerships with tech recruiters to secure
    sponsorships for hackathons and career fairs.}
\resumeItemListEnd
\resumeSubHeadingListEnd

\end{document}